---
title: "Assignment 3 - Part 1"
author: "Tal Barami & Yair Ganon"
date: "December, 2017"
output: html_document
---

### Getting started 

# Setting a working directory:
```{r}
folder = 'C:\\Users\\Tal\\Dropbox\\Semester 7\\Application of Data Analysis Methods\\Assignments\\3\\part1'
setwd(folder)

knitr::opts_knit$set(root.dir = folder)
```

# Install & load igraph:
```{r}
#install.packages("igraph")
library(igraph)
```

# Load the data files & create the graph:
```{r}
g.data <- read.csv('ga_edgelist.csv', header=TRUE, stringsAsFactors=FALSE)
g.vrtx <- read.csv('ga_actors.csv', header=TRUE, stringsAsFactors=FALSE)
g <- graph.data.frame(g.data, vertices=g.vrtx, directed=FALSE)

plot(g, vertex.size = 4, vertex.label.dist = 2, asp = F)
```
### Q1a:

# Find & plot the largest component:
```{r}
g.components <- components(g)
largest_component <- which(g.components$membership == which.max(g.components$csize))
g.largest_component <- induced_subgraph(g, largest_component)

plot(g.largest_component, vertex.size = 4, vertex.label.dist = 2, asp = F)
```

#Calculate the betweenness centrality using the igraph method:
Graph is not directed, without weights on the edges, no need to normalize the result.
```{r}
bc <- betweenness(g.largest_component, directed = FALSE, weights = NULL, normalized = FALSE)
sort(bc, decreasing = T)[1:1]
```

#Calculate the closeness centrality using the igraph method:
There are no weights on the edges, no need to normalize the result.
```{r}
cc <- closeness(g.largest_component, weights = NULL, normalized = FALSE)
sort(cc, decreasing = T)[1:1]
```

# Finally, calculate the eigen centrality using the igraph method:
Graph is not directed, without weights on the edges, we were asked for the real value, so no need to scale the result.
```{r}
ec <- eigen_centrality(g.largest_component, directed = FALSE, weights = NULL, scale = FALSE, options = arpack_defaults)$vector
sort(ec, decreasing = T)[1:1]
```

## Results:
#The character with the highest betweenness centrality is Sloan with 115.36667
#The character with the highest closeness centrality is Torres with 0.01754386
#The character with the highest eigen vector centrality is Karev with 0.5027688



### Q1b:

# 1. We'll use Girvan-Newman community detection:
```{r}
girvan_newman <-  edge.betweenness.community(g)
girvan_newman
```

# Define a modularity measure that measures the quality of a network partition:
```{r}
#modularity for each phase of the previous algorithm
girvan_newman$modularity
#best modularity score
max(girvan_newman$modularity)
#index (phase, i.e. partitioning) with the best score
which.max(girvan_newman$modularity)
```

## Grant each node a color defined by partitions, using the membership function that returns community ids for each vertex, according to our clustering model object:
```{r}
#Store cluster ids for each vertex
gn_color <- membership(girvan_newman)
head(gn_color)
```

# Then, set the node's color (vertex.color) accordingly:
```{r}
plot(g, vertex.size = 4, vertex.label.dist = 2, asp = F, vertex.color = gn_color)
```

## Results:
# There are 7 communities: 1[8], 2[5], 3[5], 4[4], 5[3], 6[3], 7[4]
# This algotithm yields modularity of: 0.5774221

# 2. We'll use the fastgreedy community detection:
```{r}
g.simple <- simplify(g)
fastgreedy <- fastgreedy.community(g.simple)
```


# Define a modularity measure that measures the quality of a network partition:
```{r}
fastgreedy$modularity
max(fastgreedy$modularity)
which.max(fastgreedy$modularity)
```

## Grant each node a color defined by partitions, using the membership function that returns community ids for each vertex, according to our clustering model object:
```{r}
fg_color <- membership(fastgreedy)
head(fg_color)
```

# Then, set the node's color (vertex.color) accordingly:
```{r}
plot(g, vertex.size = 4, vertex.label.dist = 2, asp = F, vertex.color = fg_color)
```

## Results:
# There are 6 communities: 1[10], 2[5], 3[4], 4[5], 5[5], 6[3]
# This algotithm yields modularity of: 0.5947232